An Embedding Framework for Consistent Polyhedral Surrogates

### 2020-06-30 journal/poly-embed.tex
Minor tweaks for journal version

Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand when such (consistent) surrogates can and cannot be found.
For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.

@@

While property elicitation has by now an extensive literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems.
Literature directly connecting property elicitation to consistency is sparse, with the main reference being~\citet{agarwal2015consistent}.
However, they consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
\citet{finocchiaro2020indirect}\jessiet{neurips 2020 paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum.

@@

For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms can be thought of as minimizing a surrogate loss function with better optimization qualities, e.g., convexity.
Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
After introducing notation, and terminology from property elicitation, we thus give a sufficient condition for consistency (Def.~\ref{def:calibrated}) which depends solely on the conditional distribution over $\Y$.

@@

Let $\Y$ be a finite outcome (label) space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting.

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ (and the infimum is over $\R$).

@@

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
\proposedadd{While the definition of ``optimal'' is unclear right now, but we shortly introduce loss functions that are associated with a given property.
In general, by optimal, we mean minimizing this associated loss function in expectation over $p$.}
Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

Note that it is not clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from clear.
We address the question of when embeddings lead to calibrated links in Section~\ref{sec:calibration}.
%\bo{I think in Section \ref{sec:calibration} ?}

To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
% First, consider that
% \begin{align*}
% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
% \end{align*}
% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
\[
\prop{\ellzo}(p) = \begin{cases}
1 & p_1 > 1/2 \\
\{-1,1\} & p_1 = 1/2\\
-1 & p_1 < 1/2
\end{cases}
\qquad
\prop{L_{hinge}}(p) = \begin{cases}
[1,\infty) & p_1 = 1\\
1 & p_1 \in (1/2,1) \\
[-1,1] & p_1 = 1/2\\
-1& p_1 \in (0, 1/2)\\
(-\infty, -1]& p_1 = 0
\end{cases}~.
\]
% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; in Section~\ref{sec:calibration} we show that, perhaps surprisingly, all embeddings lead to calibration with an appropriate link.

@@

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.

@@

\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.  Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency. \jessie{Added a few sentences above, when talking about consistency vs calibration.}}

@@

\btw{Cut summary for now (Why is this cool?)}
\jessiet{Jessie: added a bit to say why this is cool.}
\proposedadd{We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.}

@@

\section{Embedding properties}\label{sec:embed-props}
%\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
%\raf{Please fix refs, maybe by removing the duplicates from the appendix}
\jessie{Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	\proposedadd{Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.}
\end{definition}

By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
\proposedadd{However, we should observe that this statement is not immediately an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points; i.e. that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.  
However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.}

\jessiet{Lemma new to journal version}
\begin{lemma}\label{lem:embed-defs-equiv}
%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
  \raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
  	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.

@@

    To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

%    \hrule
%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
\end{proof}

Because of this Lemma, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
Moreover, we can assume that finite properties are non-redundant without much loss of generality.
\begin{definition}[Finite property, non-redundant]
	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
\end{definition}

@@

Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.\btw{Should this section be before or after embedding losses, since the results here are used in the proofs in the embedding losses section?}
The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).

@@

@@

\jessie{ADDITIONS HERE:}
\btw{Again: figures/an example might help clarify this}
\btw{Jessie: Can/should we move this Lemma above Prop 3 since it is used in the proof of Prop 3?}
When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
  \raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional. 
	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
  \raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:
	First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
	Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

@@

\jessie{Added from COLT-19 but not discussed in COLT-20.  Suggest removing this for 1. clarity, and 2. lack of definitions.  If we do keep it, it should move sections though.}

\begin{proposition}
	Let $L$ elicit $\Gamma:\simplex \toto \reals^d$ which embeds a finite property $\gamma$.
	Then there is a calibrated\jessie{formerly separated?} link from $\Gamma$ to $\gamma$.
\end{proposition}
\begin{proof}
	Let $\gamma: \simplex \toto \R$.
	Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r \in \R\}$.
	We conclude that for any $u \in \reals^d$, there is a calibrated link from $\Gamma$ to $\gamma$.
\end{proof}

@@

	\jessie{Expand this paragraph to 4-5 lines and remove word ``calibrated''}
	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a calibrated link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a calibrated link from $\gamma'$ to $\gamma$:
	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))}$.
	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
\end{proof}

@@

\subsection{Inconsistency of top-$k$ losses}
% 7.14.19- proposed version for arXiv
\btw{The story we discussed: YK show $L'$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?  (It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}

>>>>

Convex surrogate losses are a central building block in machine learning for finite prediction problems such as classification and structured prediction tasks.
A growing body of work seeks to design and analyze convex surrogates for given loss functions, and more broadly, understand the best empirical risk minimization bounds that can found for a surrogate, for which consistency is a necessary condition.
For example, recent work has developed tools to bound the required number of dimensions of the surrogate's hypothesis space~\cite{frongillo2015elicitation,  ramaswamy2016convex}.
Yet in some cases these bounds are far from tight, such as for \emph{abstain loss} (classification with an abstain option)~\citep{bartlett2008classification,yuan2010classification,ramaswamy2016convex,ramaswamy2018consistent,zhang2018reject}.
Furthermore, the kinds of strategies available for constructing surrogates, and their relative power, are not well understood.

@@

While property elicitation has by now an extensive literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting,gneiting2011making,steinwart2014elicitation,frongillo2015vector-valued,fissler2016higher,lambert2018elicitation}, these works are mostly concerned with point estimation problems.
Literature directly connecting property elicitation to consistency is sparse.
However,~\citet{agarwal2015consistent} consider single-valued properties in finite outcome settings, whereas finite properties elicited by general convex losses are necessarily set-valued.
\citet{finocchiaro2020indirect}\jessiet{neurips 2020 paper; might need to throw on arxiv if we want this ref.} additionally relates indirect property elicitation to consistency in finite outcome settings when one is given either a target loss or property in both discrete and continuous prediction settings, assuming surrogates attain their infimum.

@@

For discrete prediction problems like classification, due to hardness of directly optimizing a given discrete loss, many machine learning algorithms can be thought of as minimizing a surrogate loss function with better optimization qualities, e.g., convexity.
Of course, to show that this surrogate loss successfully addresses the original problem, one needs to establish consistency, which depends crucially on the choice of link function that maps surrogate reports (predictions) to original reports.
After introducing notation, and terminology from property elicitation, we study \emph{calibration} (Definition~\ref{def:calibrated}), which is equivalent to consistency in finite settings~\citep{bartlett2006convexity,tewari2007consistency} and depends solely on the conditional distribution over $\Y$.

@@

Let $\Y$ be a finite label space, and throughout let $n=|\Y|$.
The set of probability distributions on $\Y$ is denoted $\simplex\subseteq\reals^{\Y}$, represented as vectors of probabilities.
We write $p_y$ for the probability of outcome $y \in \Y$ drawn from $p \in \simplex$.
We first discuss the conditional setting, with just labels $\Y$ and no features $\X$, and show in \S~\ref{sec:links-embeddings} how these notions relate to the usual $\X\times\Y$ setting considering features.

We assume that a given discrete prediction problem, such as classification, is given in the form of a \emph{discrete loss} $\ell:\R\to\reals^\Y_+$, which maps a report (prediction) $r$ from a finite set $\R$ to the vector of loss values $\ell(r) = (\ell(r)_y)_{y\in\Y}$ for each possible outcome $y\in\Y$.
We will assume throughout that the given discrete loss is \emph{non-redundant}, meaning every report is uniquely optimal (minimizes expected loss) for some distribution $p\in\simplex$.
Similarly, surrogate losses will be written $L:\reals^d\to\reals^\Y_+$, typically with reports written $u\in\reals^d$.
\btw{Cut generic loss}%(A generic loss will be written $L:\R\to\reals^\Y$.)
We write the corresponding expected loss when $Y \sim p$ as $\inprod{p}{\ell(r)}$ and $\inprod{p}{L(u)}$.
The \emph{Bayes risk} of a loss $L:\reals^d\to\reals^\Y_+$ is the function $\risk{L}:\simplex\to\reals_+$ given by $\risk{L}(p) := \inf_{u\in\reals^d} \inprod{p}{L(u)}$; naturally for discrete losses we write $\risk{\ell}$ with the infimum over $\R$.

@@

Intuitively, $\Gamma(p)$ is the set of reports which should be optimal for a given distribution $p$, and $\Gamma_r$ is the set of distributions for which the report $r$ should be optimal.
In general, by optimal, we mean minimizing an associated loss function in expectation over $p$, which we formalize shortly.
Note that our definitions align such that discrete losses elicit finite properties; both are non-redundant in the correct senses.
For example, the \emph{mode} is the %finite
property $\mode(p) = \argmax_{y\in\Y} p_y$, and captures the set of optimal reports for 0-1 loss: for each distribution over the labels, one should report the most likely label.
In this case we say 0-1 loss \emph{elicits} the mode, as we formalize below.
% This terminology comes from the information elicitation \jessiet{information vs property... do we care?}\raft{we could also say economics literature; not ``property'' though since that doesn't offer an explanation of the word ``elicits''} literature~\citep{savage1971elicitation,osband1985information-eliciting,lambert2008eliciting}, in which a report $r$ is elicited from some forecaster by scoring her with a loss on the observed outcome $y$.

@@

It is not immediately clear if embeddings give rise to calibrated links; indeed, apart from mapping the embedded points back to their original reports via $\psi(\varphi(r)) = r$, how to map the remaining values is far from obvious.
We address the question of when embeddings lead to calibrated links in \S~\ref{sec:calibration}.
%\bo{I think in Section \ref{sec:calibration} ?}

To illustrate the idea of embedding, let us examine hinge loss in detail as a surrogate for 0-1 loss for binary classification.
Recall that we have $\R = \Y = \{-1, +1\}$, with $\hinge(u)_y = (1 - uy)_+$ and $\ellzo(r)_y := \Ind{r\neq y}$, typically with link function $\psi(u) = \sgn(u)$.
We will see that hinge loss embeds (2 times) 0-1 loss, via the embedding $\varphi(r) = r$.
For condition (i), it is straightforward to check that $\hinge(r)_y = 2\ellzo(r)_y$ for all $r,y\in\{-1,1\}$.
% First, consider that
% \begin{align*}
% 	\ellzo(-1) = (0,1) && \ellzo(1) = (1,0)\\
% 	L_{hinge}(-1) = (0,2) && L_{hinge}(1) = (2,0)\\
% \end{align*}
% Therefore, $L_{hinge}$ is twice $\ellzo$ for each $r \in \R$.
For condition (ii), let us compute the property each loss elicits, i.e., the set of optimal reports for each $p$:
\[
\prop{\ellzo}(p) = \begin{cases}
1 & p_1 > 1/2 \\
\{-1,1\} & p_1 = 1/2\\
-1 & p_1 < 1/2
\end{cases}
\qquad
\prop{L_{hinge}}(p) = \begin{cases}
[1,\infty) & p_1 = 1\\
1 & p_1 \in (1/2,1) \\
[-1,1] & p_1 = 1/2\\
-1& p_1 \in (0, 1/2)\\
(-\infty, -1]& p_1 = 0
\end{cases}~.
\]
% Now, take the embedding $\varphi$ to be the identity.  % := r$ if $r \in [-1,1]$, and $\sgn(r)$ otherwise.
In particular, we see that $-1 \in \prop{\ellzo}(p) \iff p_1 \in [0, 1/2] \iff -1 \in \prop{\hinge}(p)$, and $1 \in \prop{\ellzo}(p) \iff p_1 \in [1/2,1] \iff 1 \in \prop{\hinge}(p)$.
With both conditions of Definition~\ref{def:loss-embed} satisfied, we conclude that $\hinge$ embeds $2\ellzo$.
In this particular case, it is known $(\hinge,\psi)$ is calibrated for $\psi(u) = \sgn(u)$; in \S~\ref{sec:calibration} we show that, perhaps surprisingly, all embeddings lead to calibration with an appropriate link.

@@

    \btw{RF: This is on the informal side, mostly because of the ``working in the affine hull'' bit.  It can all be formalized though, probably should be for the journal version: just take an appropriate linear projection of $\reals^n$ to $\reals^{n-1}$, and work with the projected versions of everything, and then project back.}
  For the reverse implication, assume that $\risk{L} = \risk{\ell}$.
  In what follows, we implicitly work in the affine hull of $\simplex$ \proposedadd{by projecting into $\reals^{n-1}$}, so that interiors are well-defined, and $\risk{\ell}$ may be differentiable on the (relative) interior of $\simplex$.
  Since $\ell$ is discrete, $-\risk{\ell}$ is polyhedral as the pointwise maximum of a finite set of linear functions.
  The projection of its epigraph $E_\ell$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer}, whose cells are full-dimensional and correspond to the level sets $\gamma_r$ of $\gamma = \prop{\ell}$.

@@

%\btw{RF: matching risks is not necessary for \emph{consistency}, as evidenced by logistic loss for 0-1 loss.  Maybe we should just make the observation, earlier on, that \emph{embedding} is not necessary for consistency. \jessie{Added a few sentences above, when talking about consistency vs calibration.}}

@@

%\btw{Cut summary for now (Why is this cool?)}
%\jessiet{Jessie: added a bit to say why this is cool.}
We will see that embedding implies the existence of a consistent surrogate and link, so this result tells us that, for discrete losses, the embedding framework is sufficient to understand the existence of consistent surrogates for the given loss.
Even if there is a smooth surrogate for a given discrete loss, there is also a polyhedral loss that is calibrated for the given loss.
What's more is that there is a polyhedral \emph{embedding} that is calibrated for the discrete loss.

@@

\section{Embedding properties}\label{sec:embed-props}
%\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
%\raf{Please fix refs, maybe by removing the duplicates from the appendix}
\jessiet{Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.
\end{definition}

By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
This statement is not immediately equivalent because property embedding does not capture the requirement of matching losses on embedded points; i.e. that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.  
However, Lemma~\ref{lem:embed-defs-equiv} shows an equivalence follows without loss of generality.

\jessiet{New to journal version}
\begin{lemma}\label{lem:embed-defs-equiv}
%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function.
	If the property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
  \raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.  Now very similar to the proof of Prop 1 forward direction.}}
  	Consider a loss $\ell : \R \to \reals_+^\Y$, defined so that $\ell : r \mapsto L(\varphi(r))$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.

@@

    To verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$ by embedding, $ \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)}$ by $L$ eliciting $\Gamma$, and $ \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$ by applying the definition of properties to the embedding definition.
%    \hrule
%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.
%
%  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
\end{proof}

By Lemma~\ref{lem:embed-defs-equiv}, we can work directly with properties and set aside the losses which elicit them, which is often more convenient.
Moreover, we can assume that finite properties are non-redundant without much loss of generality.
\begin{definition}[Finite property, non-redundant]
	A property $\gamma:\simplex\toto\R$ is \emph{redundant} if for some $r,r'\in\R$ with $r \neq r'$, we have $\gamma_r \subseteq \gamma_{r'}$, and \emph{non-redundant} otherwise.
	$\gamma$ is \emph{finite} if it is non-redundant and $\R$ is a finite set.
\end{definition}

@@

Before we state the Proposition needed to prove many of the statements in Section~\ref{sec:poly-loss-embed}, we will need to general lemmas about properties and their losses.\btw{Jessie: Should this section be before or after embedding losses, since the results here are used in the proofs in the embedding losses section?}
The first follows from standard results relating finite properties to power diagrams (see Theorem~\ref{thm:aurenhammer}), and its proof is omitted.
The second is closely related to the definition of the trim operator: it states that if some subset of the reports are always represented among the minimizers of a loss, then one may remove all other reports and elicit the same property (with those other reports removed).

@@

\btw{Jessie: Again, figures/an example might help clarify this}
When a property $\Gamma$ embeds a finite property $\gamma$, we can show that the level sets of $\gamma$ correspond exactly to their embedded level sets of $\Gamma$, and that these embedded level sets are exactly $\trim(\Gamma)$.
\btw{Jessie: This lemma new to journal version}
\begin{lemma}\label{lem:embedded-level-sets-trim}
	Let $\Gamma$ be an elicitable property.
	If $\Gamma$ embeds a finite property $\gamma : \simplex \toto \R$ by the injection $\varphi$, then $\{\gamma_r : r \in \R\} = \{\Gamma_u : u \in \varphi(\R)\} = \trim(\Gamma)$.
\end{lemma}
\begin{proof}
	Let $L$ elicit $\Gamma$.
	Take $\ell$ to be the loss embedded by $L$ from Lemma~\ref{lem:embed-defs-equiv}.
	Moreover, by Proposition~\ref{prop:embed-bayes-risks}, we have $\risk{L} = \risk{\ell}$.
	\raft{Implicitly? Justify the claim.  \jessie{In definition of finite properties, we say that we assume we are talking about non-redundant.}}
	As $\gamma$ is finite (and non-redundant by assumption), we know that each level set of $\gamma$ must be full-dimensional. 
	For all $r \in \R$, we know $\gamma_r = \Gamma_{\varphi(r)}$, so we must also have $\Gamma_{\varphi(r)}$ full-dimensional.
	Moreover, we have $\{\gamma_r : r \in \R\} = \{\Gamma_{\varphi(r)} : r \in \R\}$ as a corollary since this is true for each $r \in \R$.
	\raft{The main action is here.  (1) Epigraph of $-\risk{L}$. (2) There is really only one case: every level set is a face of the power diagram, which must be contained (weakly, so $\subseteq$) in a facet. (3) To show that level sets are faces, you'll want to appeal to some piece of a proof in the prev section.}
	Since the cell $\Gamma_{\varphi(r)}$ is the projection of a facet of the epigraph of $\risk{L}$, which is concave, any other level set intersecting $\Gamma_{\varphi(r)}$ can be considered in one of two cases:
	First, if the level set $\Gamma_u$ (for $u \not \in \varphi(\R)$) is a projection of a lower-dimensional face of $\risk{L}$, which is contained in a facet of the epigraph.
	Therefore, we must have $\Gamma_u \subset \Gamma_{\varphi(r)}$ for some $r \in \R$, and therefore $\Gamma_u \not \in \trim(\Gamma)$.

@@

@@

@@

	\raft{I might be delusional, but this second part ended up being much slicker than I'd thought, by essentially chaining definitions and maps.  Please check!}
	For the second part, let $\gamma':\simplex\toto\R'$ be the finite elicitable property embedded by $L$, with embedding $\varphi:\R'\to\reals^d$, and let $\psi$ be a link to a non-redundant elicitable property $\gamma:\simplex\toto\R$.
	Then letting $\psi' = (\psi \circ \varphi):\R'\to\R$, we see that $\psi'$ is a link from $\gamma'$ to $\gamma$:
	for all $r'\in\R'$, we have $\gamma'_{r'} = \prop{L}_{\varphi(r')} \subseteq \gamma_{\psi(\varphi(r'))} = \gamma_{\psi'(r')}$.
	In particular, $\gamma'$ refines $\gamma$, and as $\gamma'$ is finite, $\gamma$ must be finite.
\end{proof}

@@

\subsection{Inconsistency of top-$k$ losses}
% 7.14.19- proposed version for arXiv
%\jessiet{The story we discussed: YK show $L'$ is inconsistent.  Our framework lets us ask: with what discrete loss \emph{is} $L'$ consistent?  (It also assures us that $L'$ is consistent for something...) Oh look, $L'$ embeds something which is $\elltopk$ plus some other term, so (a) we can see very clearly what $L'$ ``is doing'', and (b) we can see where to look for distributions yielding inconsistency, namely ones for which we actually prefer to report a set with $|r|<k$.}
